### 2016-08-02 R/ITHIM.Rmd
Minor update to ITHIM.Rmd

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("plyr")
```

@@

convertToAgeClass <- function(age){
  age <- as.numeric(age)
  agecat <- ifelse( age <= 4, "00-04", ifelse( age <= 14, "05-14", ifelse( age <= 29, "15-29", ifelse( age <= 44, "30-44", ifelse( age <= 59, "45-59", ifelse( age <= 69, "60-69", ifelse( age <= 79, "70-79", ifelse( age > 80, "80+", NA))))))))
  return(agecat)
}

@@

(foo <- ddply(NHTS, .(SEX, AGE, AT), summarise,
             sum = sum(TRVL_MIN, na.rm=T)
             ))

@@

>>>>

```{r libs, eval = TRUE, echo = FALSE, results = "hide", warning = FALSE, error = FALSE, message = FALSE}
options(repos='http://cran.rstudio.com/')
library("ggplot2")
library("reshape2")
library("dplyr")
```

@@

@@

@@

NHTS %>% group_by(SEX, AGE) %>% summarize(trips = n())
